\documentclass[12pt]{article}

\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{titling}
\usepackage{times}
\usepackage{anysize}
\marginsize{2cm}{2cm}{2cm}{3cm}
%\onehalfspace
%\doublespace
\setlength{\parindent}{0.8cm}
%\setlength{\parskip}{0.2\baselineskip}
%\setlength{\topmargin}{2cm}
%\setlength{\textheight}{25cm}
%\setlength{\textwidth}{14cm}
%\setlength{\oddsidemargin}{2cm}
%\setlength{\evensidemargin}{2cm}
\usepackage{fancyhdr}
\pagestyle{fancy}

\newcommand{\note}[1]{\textbf{\textit{#1}}}
\newcommand{\astar}{A$^*$}


\newtheorem{theorem}{Theorem}
\newtheorem{observation}{Observation}
\newtheorem{corollary}{Corollary}

\linespread{1.3}
\begin{document}
\title{Broader Impacts Statement \\ \Large{Data-and-Model Driven Reasoning, BSF Application No. 2016141}}
\date{\vspace{-0.5cm}}
\author{Roni Stern \\ Software and Information Systems Eng., Ben Gurion University of the Negev
        \and Brendan Juba \\ Computer Science, Washington University in St. Louis}



\maketitle

%\begin{center}
%\LARGE{Broader Impact Statement}
%\end{center}
% BSF Instructions:
%This file should include the words 'Broader Impacts Statement' in the heading. The following information should be included: the full title of the proposed application, which should be brief, meaningful and suitable for use in the general media; the application number supplied by the system; and the names and affiliations of the principal investigators.
%An impact statement of about 250 words or less is required. Please address the broader impact and importance (social and/or economic and/or scientific value) of the proposed research.

%While in the proposed research we will focus on two specific problems -- planning and diagnosis -- the impact is expected to be much wider. 

%First, model-based and data-driven methods have been used to a much wider range of problems, such as plan recognition, coordination of multi-agent systems, and scheduling. We expect that the foundations we will establish in the proposed research for integrating model and observations will carry over to other tasks. 
%The tasks of planning and diagnosis have numerous applications beyond academia; for example, autonomous vehicles and other robots require planning algorithms, and diagnosis algorithms have obvious applications as tools in engineering for debugging. Indeed, we note that we will include an evaluation of our diagnosis algorithms in particular on such engineering problems. We expect the algorithms that we develop for planning and diagnosis to improve the speed, quality, and breadth of applicability of these algorithms.
Automated planning has numerous applications beyond academia, e.g., in the development of autonomous vehicles and other robots. Similarly, automated diagnosis also has obvious applications, e.g., in the maintenance of complex systems and their software. Indeed, we intend to evaluate our diagnosis algorithms in particular on such engineering problems. %and problems a. 
We expect the algorithms that we develop for planning and for diagnosis to improve the speed, quality, and breadth of applicability of these algorithms. 

The PAC search framework we will develop will open up the field of heuristic search to the notion of probabilistic guarantees, which will allow search algorithms in general to scale to much larger problems while still preserving a useful notion of solution quality. 

Also, our methods for integrating models and data may carry over to other tasks such as coordination of multi-agent systems and scheduling with their own real-world applications. By studying and understanding the effect of having a partial model on the theoretical limits of what can be learned from data, one can decide the cost-effectiveness of generating such a model. 
This is especially important since modeling the world is notoriously difficult, and choosing what not to model is a key problem in practical applications of AI. 

Finally, most funds are requested to support graduate students, reflecting our focus on education and our commitment to training the next generation of researchers. 



\end{document}

